Vertical and oblique transmission with fluctuating transmission

### 2018-03-20 ms/fluctuating_oblique.tex
new discussion paragraphs; citations

There has been much less theory developed for fluctuating transmission.
Nevertheless, if we assume that social learning can be affected by frequency of interactions~\citep{VanSchaik2003}, weather~\citep{Phithakkitnukoon2012}, food availability, population density~\citep{Aureli1997a}, or even political atmosphere, then it is reasonable that the mode and rate of transmission will fluctuate over time. 
For example, it may be the case that during cold seasons offspring are more likely to stay close to their parents and therefore learn vertically, whereas during warm seasons they are more likely to wander and interact with other adults and therefore learn obliquely.

@@

% Face book rural internet
% National service - Israel, Singapore
% Immigrtion - draught
% Opening schools, universities
% sending students abroad, bringing experts from abroad
% foreign labor
% refugees
% hunter-gatherers/chimps increase habitat in years with less food production
% religion - dark ages etc.

@@

\bibliographystyle{agsm}
\bibliography{/Users/yoavram/Documents/library}
%\bibliography{fluctuating_oblique}

>>>>

There has been much less theory developed for fluctuating transmission.
Nevertheless, if we assume that social learning can be affected by frequency of interactions~\citep{VanSchaik2003}, weather~\citep{Phithakkitnukoon2012}, stress~\citep{Farine2015}, food availability, population density~\citep{Aureli1997a}, or even political atmosphere, then it is reasonable that the mode and rate of transmission will fluctuate over time. 
For example, it may be the case that during cold seasons offspring are more likely to stay close to their parents and therefore learn vertically, whereas during warm seasons they are more likely to wander and interact with other adults and therefore learn obliquely.

@@

One caveat of our model is the use of the ``phenotypic gambit'' -- the assumption that the transmission mode itself is strictly vertically transmitted.
Although there is evidence that the tendency to use different learning mechanisms is genetically transmitted~\citep{Foucaud2013}, this assumption may be a challenged: at least in humans, individuals may be able to learn how and when to learn, in what has been called ``social learning of social learning''~\citep{Mesoudi2016}.
It is also possible that the transmission mode is regulated.
For example, \citet{Farine2015} found that zebra fish switch from vertical to oblique transmission after exposure to stress hormones.
Our model accounts for cases in which the entire population changes its transmission mode due to stress, but not for cases in which only some individuals do so.

Another extension of our model could incorporate more sophisticated oblique transmission schemes.
For example, conformity -- preference for learning a frequent phenotype -- has been demonstrated in wild vervet monkeys~\citep{VanDeWaal2013} and birds~\citep{Aplin2015}.
We suggest that the oblique transmission mode can also fluctuate over time, so that individuals can, for example, conform to the frequent phenotype under benign conditions, and prefer a rare phenotype under stressful conditions.

% Facebook rural internet
% National service - Israel, Singapore
% Immigrtion - draught
% Opening schools, universities
% sending students abroad, bringing experts from abroad
% foreign labor
% refugees
% hunter-gatherers/chimps increase habitat in years with less food production
% religion - dark ages etc.

@@

\bibliographystyle{agsm}
%\bibliography{/Users/yoavram/Documents/library}
\bibliography{fluctuating_oblique}
